Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd
added population to data

>>>>

## Population {#population}

The “population” variable in the dataset represents the status of each
entry, categorizing participants as “lv” (likely voters) or “rv”
(registered voters). They represent different levels of participation
and potential voting behavior. Likely voters are individuals who are not
only registered but are statistically more likely to vote based on historical
data or survey responses. In contrast, registered voters include all
individuals who are eligible to vote, regardless of their likelihood
of participation.
